---
title: "Presentation Ninja"
subtitle: "&#x2694;&#xFE0F; xaringan +<br/>&#x1F60E; xaringanthemer"  
author: 
  - "Dea Avega Editya"
  - "M. Soban Q."
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    seal: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE, digits = 2)

knitr::opts_chunk$set(warning = FALSE, message = FALSE, error = FALSE, tidy.opts = list(width.cutoff=60), tidy=TRUE)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#1381B0",
  secondary_color = "#FF961C",
  inverse_header_color = "#FFFFFF"
)

library(readr)
library(dplyr)
library(tidyverse)
library(lubridate)
library(fontawesome)
library(plotly)
```


.center[

## CWD Group Presentation

.middle[
.pull-left[
<img src = "vega.png" , width = 40%>  
Dea Avega Editya]

.pull-right[
<img src = "sobyan.jpg" , width = 40%>  
M. Soban Qasim
]
  
  
      
Melbourne, `r Sys.Date()` 
]
  
  
]




---
.center[
### Research question:
]

.center[
Does Melbourne really have 4 (four) seasons in a day?  
]
--
.center[
What makes a season anyway?  
]
--
.center[
### Secret recipe to make a distinguish season
]
--
.center[
<img src = "hot.png" width = 10%> 
<img src = "plus.png" width = 10%> 
<img src = "drop.png" width = 10%>
]
--
.center[
<img src = "https://wi-images.condecdn.net/image/doEYpG6Xd87/crop/2040/f/weather.jpg" width = 40%>
]

---

### Let's Try to Find Out! `r fa("search", fill = "lightred")`

#### Steps Revealed

To find the answer for our research question, we need to compare temperature in a regular day to 4 different typical temperature of each season.  
It should be also done for humidity!   

--
  
Therefore, we will:
1. Explore data of temperature & humidity in the dataset
1. Count average number per hour for these variables
1. Compare the number to threshold
1. Plot the comparison

---

### Loading Dataset of Melbourne Sensor

```{r echo = TRUE}
melb_sensor <- read.csv("Microclimate_Sensor_Readings.csv")

melb_temp <- melb_sensor %>% 
  filter(units %in% c("C", "%")) %>%
  mutate(time = ymd_hms(local_time)) %>% 
  mutate(hour = lubridate::hour(time), date = date(time), month = month(time))

```

Data source: [melbourne.vic.gov.au](https://data.melbourne.vic.gov.au/Environment/Microclimate-Sensor-Readings/u4vh-84j8?src=featured_banner)

Data is updated hourly hence consist of 1.34 million rows!  
There are 7 variables inside.

.center[
<img src = "columns.PNG" width = 80%>
]
---

### Finding Typical Temperature & Humidity for Each Season

```{r echo = FALSE, warning = FALSE}
# average in seasons
# summer
ave_summer <- melb_temp %>% 
  filter(units == "C", type == "TPH.TEMP-EPA-1h", month %in% c(12, 1, 2)) %>% 
  summarise(average = mean(value))

ave_spring <- melb_temp %>% 
  filter(units == "C", type == "TPH.TEMP-EPA-1h", month %in% c(9, 10, 11)) %>% 
  summarise(average = mean(value))

ave_autumn <- melb_temp %>% 
  filter(units == "C", type == "TPH.TEMP-EPA-1h", month %in% c(3, 4, 5)) %>% 
  summarise(average = mean(value))

ave_winter <- melb_temp %>% 
  filter(units == "C", type == "TPH.TEMP-EPA-1h", month %in% c(6, 7, 8)) %>% 
  summarise(average = mean(value))

# rainfall / humid
ave_rainsummer <- melb_temp %>% 
  filter(type == "TPH.RH-EPA-1h", month %in% c(12, 1, 2)) %>% 
  group_by(type) %>% 
  mutate(daily_value = lag(value)) %>% 
  drop_na() %>% 
  summarise(average = mean(daily_value))

ave_rainspring <- melb_temp %>% 
  filter(type == "TPH.RH-EPA-1h", month %in% c(9, 10, 11)) %>% 
  group_by(type) %>% 
  mutate(daily_value = lag(value)) %>% 
  drop_na() %>% 
  summarise(average = mean(daily_value))

ave_rainautumn <- melb_temp %>% 
  filter(type == "TPH.RH-EPA-1h", month %in% c(3, 4, 5)) %>% 
  group_by(type) %>% 
  mutate(daily_value = lag(value)) %>% 
  drop_na() %>% 
  summarise(average = mean(daily_value))

ave_rainwinter <- melb_temp %>% 
  filter(type == "TPH.RH-EPA-1h", month %in% c(6, 7, 8)) %>% 
  group_by(type) %>% 
  mutate(daily_value = lag(value)) %>% 
  drop_na() %>% 
  summarise(average = mean(daily_value))
```

1. We will find typical temperature for each seasons in Melbourne!  

    * `r fa("sun", fill = "red")` **Summer** (December, January, February) = `r pull(ave_summer)` C 

    * `r fa("cloud-sun", fill = "blue")` **Autumn** (March, April, May) =  `r pull(ave_autumn)` C 

    * `r fa("snowflake", fill = "blue")` **Winter** (June, July, August) = `r pull(ave_winter)` C 
   
    * `r fa("seedling", fill = "green")` **Spring** (September, October, November) =`r pull(ave_spring)` C

1. Also typical humidity for each seasons in Melbourne  

    * `r fa("sun", fill = "red")` **Summer** (December, January, February) = `r pull(ave_rainsummer)` %  

    * `r fa("cloud-sun", fill = "blue")` **Autumn** (March, April and May) = `r pull(ave_rainautumn)` % 
   
    * `r fa("snowflake", fill = "blue")` **Winter** (June, July and August) = `r pull(ave_rainwinter)` %  
   
    * `r fa("seedling", fill = "green")` **Spring** (September, October and November) =`r pull(ave_rainspring)` %


---

### Four Seasons in a Day - Melbourne Story 

#### Is that true that we can feel four seasons in a day in Melbourne?

<img src = "hot.png" width = 5%> Average Hourly Temperature in Melbourne

.pull-left[
```{r temp, eval = FALSE}

melb_temp %>% 
  filter(units == "C") %>% 
  group_by(hour) %>% 
  summarise(ave_val = mean(value, na.rm = TRUE)) %>% 
  ggplot(aes(x = hour, y = ave_val))+
    geom_col(fill = "grey")+
    geom_hline(yintercept =  pull(ave_autumn), color = "brown", size = 1)+
    geom_hline(yintercept = pull(ave_summer), color = "red", size = 1)+
    geom_hline(yintercept = pull(ave_winter), color = "blue", size = 1)+
    geom_hline(yintercept = pull(ave_spring), color = "green", size = 1)+
    
  geom_text(aes(23, pull(ave_autumn),label = "autumn", vjust = -1))+
  geom_text(aes(23, pull(ave_summer),label = "summer", vjust = 1))+
  geom_text(aes(23, pull(ave_spring),label = "spring", vjust = 1))+
  geom_text(aes(23, pull(ave_winter),label = "winter", vjust = -1))+
  theme_minimal()+
  xlab("Time Hour")+
  ylab("Hourly Average Temperature (C)") + theme(axis.title  = element_text(size = 15), axis.text = element_text(size = 15))


```
]

.pull-right[
```{r plot-out, ref.label = "temp", echo= FALSE}

```
]

---

### Four Seasons in a Day - Melbourne Story 

#### Is that true that we can feel four seasons in a day in Melbourne?

<img src = "drop.png" width = 5%> Average Hourly Humidity in Melbourne

.pull-left[
```{r rain, eval = FALSE}
melb_temp %>% 
  filter(type == "TPH.RH-EPA-1h") %>% 
  group_by(hour) %>% 
  summarise(ave_humid = mean(value, na.rm = TRUE)) %>% 
  ggplot(aes(x = hour, y = ave_humid)) +
    geom_col(fill = "grey") +
  geom_hline(yintercept =  pull(ave_rainautumn), color = "brown", size = 1) +
    geom_hline(yintercept = pull(ave_rainsummer), color = "red", size = 1) +
    geom_hline(yintercept = pull(ave_rainwinter), color = "blue", size = 1) +
    geom_hline(yintercept = pull(ave_rainspring), color = "green", size = 1) +
  geom_text(aes(23, pull(ave_rainautumn),label = "autumn", vjust = -.7))+
  geom_text(aes(23, pull(ave_rainsummer),label = "summer", vjust = -.5))+
  geom_text(aes(23, pull(ave_rainspring),label = "spring", vjust = 1))+
  geom_text(aes(23, pull(ave_rainwinter),label = "winter", vjust = -.5))+
  theme_minimal() +
  xlab("Time Hour") +
  ylab("Hourly Relative Humidity (%)") + theme(axis.title  = element_text(size = 15), axis.text = element_text(size = 15))
```
]

.pull-right[
```{r plot-out2, ref.label= "rain", echo = FALSE}

```
]

---

### Conclusion

From temperature & humidity plots we know that:

--
  
* There is a huge fluctuation both in temperature and humidity during a day

--

* People are right when they say that there are 4 seasons in a day in Melbourne!

.top[
```{r season, eval=TRUE, message=FALSE, warning = FALSE}
humi <- melb_temp %>% 
  filter(type == "TPH.RH-EPA-1h") %>% 
  group_by(hour) %>% 
  summarise(ave_humid = mean(value, na.rm = TRUE)) 
temp <- melb_temp %>% 
  filter(units == "C") %>% 
  group_by(hour) %>% 
  summarise(ave_val = mean(value, na.rm = TRUE))
p <-  ggplot() + geom_col(data = humi, aes(x = hour, y = ave_humid, fill = "humid")) +  
  geom_col(data = temp, aes(x = hour, y = ave_val, fill = "temp"))  +
  geom_hline(yintercept =  pull(ave_rainautumn), color = "brown") +
    geom_hline(yintercept = pull(ave_rainsummer), color = "red") +
    geom_hline(yintercept = pull(ave_rainwinter), color = "blue") +
    geom_hline(yintercept = pull(ave_rainspring), color = "green") + 
    geom_hline(yintercept =  pull(ave_autumn), color = "brown")+
    geom_hline(yintercept = pull(ave_summer), color = "red")+
    geom_hline(yintercept = pull(ave_winter), color = "blue")+
    geom_hline(yintercept = pull(ave_spring), color = "green") +
  theme_minimal() +
  xlab("Time Hour") + ylab("Hourly Relative Humidity (%) & Hourly Average Temperature (C)") + theme(axis.title  = element_text(size = 15), axis.text = element_text(size = 15), legend.title = element_blank(),legend.text = element_text (size = 15))
```
]

---

## What do you guys think? 

.center[
```{r plot-out3, echo = FALSE, warning = FALSE, message=FALSE}
p
```
]

---

.center[
# Thank You!

## Questions?
]


.center[
<img src = "any-questions.gif" , width = 60%>  

]

